---
title: "Migration Status Report"
numbered: true
---

```{r}
#| include: false
#| message: false
#| warning: false

# Obtain the api keys for each connect
server = "https://dap-prd2-connect.azure.defra.cloud"
api_key =Sys.getenv("OLD_CONNECT_API_KEY")
newcnnctserver = "https://dash-connect-prd.azure.defra.cloud"
newcnntapikey =Sys.getenv("NEW_CONNECT_API_KEY")
#library(contentaudit)
#library(dplyr)

```

```{r, retrieving-logs-from-servers}
#| include: false
#| message: false
#| warning: false

oldcnnt_users_content <- contentaudit::fetch_users_content(connect_server = server, connect_api_key = api_key)
newcnnt_users_content <- contentaudit::fetch_users_content(connect_server = newcnnctserver, connect_api_key = newcnntapikey)


```

```{r, obtaining-master-final-data}
#| include: false
#| message: false
#| warning: false

#library(dplyr)
new_vars_data <- new_vars(newcnnt_users_content) %>%
  dplyr::mutate(new_connect = c('new_server'))

old_vars_data <- new_vars(oldcnnt_users_content)  %>%
  dplyr::mutate(old_connect = c('old_server'))

new_old_migrated_data <- dplyr::full_join(new_vars_data, old_vars_data)

```

```{r, saving-data}
#| include: false
#| message: false
#| warning: false



migration_data_detected <- contentaudit::detect_migration_and_testapps(new_old_migrated_data, threshold = 0.6)

readr::write_csv(migration_data_detected, "data/migration_data_detected.csv")
```

```{r, spot-migrated}
#| include: false
#| message: false
#| warning: false

spot_migrated <- migration_data_detected %>%
  dplyr::filter(
    migration == "migrated",
    contains_test_app_innew == FALSE,
    a_nona_account == FALSE
  ) %>%
  dplyr::count()
# there are 28 now as 22/10
```

```{r, old_server_ex_a_accounts}
#| include: false
#| message: false
#| warning: false

old_server_ex_a_accounts <- migration_data_detected %>%
  dplyr::filter(
    old_connect == "old_server",
    a_nona_account == FALSE
  ) %>%
  dplyr::count()

#there are 312 as of 22/10
```

```{r, new-apps-in-new-connect}
#| include: false
#| message: false
#| warning: false

new_apps_in_new_connect <- migration_data_detected %>%
  dplyr::filter(
    migration == "new app",
    contains_test_app_innew == FALSE,
    a_nona_account == FALSE
  ) %>%
  dplyr::count()
# there are 15 apps 
```

```{r, new_server_excl_test_app_a_accounts}
#| include: false
#| message: false
#| warning: false

filtered_data <- migration_data_detected %>%
  filter(
    new_connect == "new_server",
    migration == "migrated", 
    contains_test== FALSE,
    a_nona_account == FALSE
  )

# Count per app_mode
app_mode_counts <- filtered_data %>%
  count(app_mode, sort = TRUE)

# Total number of apps
total_apps <- filtered_data %>%
  summarise(total = n())

# Display both
#list(app_mode_counts = app_mode_counts, total_apps = total_apps)
```

```{r, old-server-excl-testapps-accounts, results='hide'}
#| echo: false
#| message: false
#| warning: false

filtered_data_old <- migration_data_detected %>%
  dplyr::filter(
    old_connect == "old_server",
    contains_test == FALSE,
    a_nona_account == FALSE
  )

# Count per app_mode
old_app_mode_counts <- filtered_data_old %>%
  dplyr::count(app_mode, sort = TRUE)

# Total number of apps
old_total_apps <- filtered_data_old %>%
  dplyr::summarise(total = n())

# Display both
list(old_app_mode_counts = old_app_mode_counts, old_total_apps = old_total_apps, app_mode_counts = app_mode_counts, total_apps = total_apps)

# Combine old and new app mode counts
combined_counts <- dplyr::full_join(
  dplyr::rename(old_app_mode_counts, old_count = n),
  dplyr::rename(app_mode_counts, new_count = n),
  by = "app_mode"
) %>%
  tidyr::replace_na(list(old_count = 0, new_count = 0)) %>%
  dplyr::mutate(
    percent_migration = dplyr::case_when(
      old_count == 0 ~ NA_real_,  # Avoid divide-by-zero
      TRUE ~ (new_count / old_count) * 100
    )
  )

# Add total row
grand_totals <- tibble::tibble(
  app_mode = "GRAND TOTAL",
  old_count = old_total_apps$total,
  new_count = total_apps$total,
  percent_migration = ceiling((total_apps$total / old_total_apps$total) * 100
))

# Final table data
final_table <- dplyr::bind_rows(combined_counts, grand_totals)
final_table




```

```{r, newserver-server-testapps-non_accounts, results='hide'}
#| echo: false
#| message: false
#| warning: false

# Filter old server apps (excluding test and nona)
filtered_data_old <- migration_data_detected %>%
  dplyr::filter(
    old_connect == "old_server",
    contains_test == FALSE,
    a_nona_account == FALSE
  )

# Filter migrated apps
filtered_data_migrated <- migration_data_detected %>%
  dplyr::filter(
    migration == "migrated",
    contains_test == FALSE,
    a_nona_account == FALSE
  )

# Filter new apps
filtered_data_new <- migration_data_detected %>%
  dplyr::filter(
    new_connect == "new_server",
    migration == "new app",
    contains_test == FALSE,
    a_nona_account == FALSE
  )

# Count per app_mode
old_counts <- filtered_data_old %>% 
  dplyr::count(app_mode, name = "old_count", sort = TRUE)

migrated_counts <- filtered_data_migrated %>% 
  dplyr::count(app_mode, name = "migrated_count")

new_counts <- filtered_data_new %>% dplyr::count(app_mode, name = "new_count")

# Combine all counts
combined <- old_counts %>%
  dplyr::full_join(migrated_counts, by = "app_mode") %>%
  dplyr::full_join(new_counts, by = "app_mode") %>%
  tidyr::replace_na(list(old_count = 0, migrated_count = 0, new_count = 0)) %>%
  dplyr::mutate(
    total_migrated = migrated_count + new_count,
    percent_migrated_total = dplyr::case_when(
      old_count == 0 ~ NA_real_,
      TRUE ~ (total_migrated / old_count) * 100
    )
  )

# Add GRAND TOTAL row
grand_totals <- tibble::tibble(
  app_mode = "GRAND TOTAL",
  old_count = sum(combined$old_count),
  migrated_count = sum(combined$migrated_count),
  new_count = sum(combined$new_count),
  total_migrated = sum(combined$total_migrated),
  percent_migrated_total = ceiling((sum(combined$total_migrated) / sum(combined$old_count)) * 100))

# Final table
final_table_new_app <- dplyr::bind_rows(combined, grand_totals)

# View result
final_table_new_app




```

## 📊 Migration Summary

Counting the migration of apps is a bit challenging due three facts:

-   users either change the names of migrated apps or

-   add similar names

-   there are test apps

Therefore different tables with different scenarios that affects the counts are considered.

::: panel-tabset
## Scenario 1

###### Counting migrated apps - but excluding the new apps

**Test apps are excluded** from counts in both Old Connect Server and New Connect Server.

Names of the **migrated apps aren't exactly the same**. Thus, similarity score was used to match names; a score above 50% counts as the same app. Username and app type were also used alongside similarity score to determine whether the app is the same or similar from the one in Old Connect.

**Total migration percentage:** `r final_table$percent_migration[final_table$app_mode == "GRAND TOTAL"]`% out of `r final_table$old_count[final_table$app_mode == "GRAND TOTAL"]`

```{r}
#| echo: false
#| message: false
#| warning: false

# Build GT table
migration_table <- gt::gt(final_table, rowname_col = "app_mode") %>%
  gt::tab_header(
    title = gt::md("📊 **App Mode Migration: New vs Old Server**")
  ) %>%
  gt::fmt_number(
    columns = gt::vars(old_count, new_count),
    decimals = 0,
    use_seps = TRUE
  ) %>%
  gt::fmt_number(
    columns = gt::vars(percent_migration),
    decimals = 1,
    use_seps = TRUE,
    suffixing = "%"
  ) %>%
  gt::cols_label(
    old_count = "Old Server",
    new_count = "New Server",
    percent_migration = "% Percent"
  ) %>%
  gt::cols_align(align = "center", columns = gt::everything()) %>%
  gt::data_color(
    columns = gt::vars(old_count, new_count, percent_migration),
    colors = scales::col_numeric(
      palette = paletteer::paletteer_d("ggsci::red_material") %>% as.character(),
      domain = NULL
    ),
    alpha = 0.8
  ) %>%
  gt::tab_footnote(
    footnote = "Test apps are excluded from counts in both Old Server and New Server.",
    locations = gt::cells_title(groups = "title")
  ) %>%
  gt::tab_footnote(
    footnote = "Apps in Old Connect Server might have different names compared to those in New Connect Server. Similarity score was used to match names; a score above 50% counts as the same app. Username and app_mode were also used to identify migrated apps.",
    locations = gt::cells_column_labels(columns = "percent_migration")
  ) %>%
  gt::tab_source_note(
    source_note = "For internal purposes only."
  ) %>%
  gt::tab_options(
    heading.background.color = "#EFFBFC",
    column_labels.background.color = "#EFFBFC",
    table.font.color = "#323232",
    table_body.hlines.color = "#989898",
    table_body.border.top.color = "#989898",
    heading.border.bottom.color = "#989898",
    table.width = "70%"
  ) %>%
  gt::opt_all_caps()

migration_table
write.csv(migration_table, "data/migration_summary.csv", row.names = FALSE)
```

[⬇️ Download Migration Summary CSV](data/migration_summary.csv)

## Scenario 2

##### Adding the new apps alongside migrated apps

**New apps (under different names) appear to be published** .

**Test apps are excluded** from counts in both Old Connect Server and New Connect Server.

Names of the **migrated apps aren't exactly the same**. Thus, similarity score was used to match names; a score above 50% counts as the same app. Username and app type were also used alongside similarity score to determine whether the app is the same or similar from the one in Old Connect.

**Total migration percentage:** `r  final_table_new_app$percent_migrated_total[final_table_new_app$app_mode == "GRAND TOTAL"]`% out of `r final_table_new_app$old_count[final_table_new_app$app_mode == "GRAND TOTAL"]`

```{r}
#| echo: false
#| message: false
#| warning: false

# Build GT table with new app and migrated columns
migration_table_new_app <- gt::gt(final_table_new_app, rowname_col = "app_mode") %>%
  gt::tab_header(
    title = gt::md("📊 **App Mode Migration: New vs Old Server**")
  ) %>%
  gt::fmt_number(
    columns = gt::vars(old_count, migrated_count, new_count, total_migrated),
    decimals = 0,
    use_seps = TRUE
  ) %>%
  gt::fmt_number(
    columns = gt::vars(percent_migrated_total),
    decimals = 1,
    use_seps = TRUE,
    suffixing = "%"
  ) %>%
  gt::cols_label(
    old_count = "Old Server",
    migrated_count = "Migrated Apps",
    new_count = "New Apps",
    total_migrated = "Total",
    percent_migrated_total = "% Percent"
  ) %>%
  gt::cols_align(align = "center", columns = gt::everything()) %>%
  gt::data_color(
    columns = gt::vars(old_count, migrated_count, new_count, total_migrated, percent_migrated_total),
    colors = scales::col_numeric(
      palette = paletteer::paletteer_d("ggsci::red_material") %>% as.character(),
      domain = NULL
    ),
    alpha = 0.8
  ) %>%
  gt::tab_footnote(
    footnote = "Test apps are excluded from counts in both Old Server and New Server.",
    locations = gt::cells_title(groups = "title")
  ) %>%
  gt::tab_footnote(
    footnote = "Apps in Old Connect Server might have different names compared to those in New Connect Server. Similarity score was used to match names; a score above 50% counts as the same app. Username and app_mode were also used to identify migrated apps.",
    locations = gt::cells_column_labels(columns = "percent_migrated_total")
  ) %>%
  gt::tab_source_note(
    source_note = "For internal purposes only."
  ) %>%
  gt::tab_options(
    heading.background.color = "#EFFBFC",
    column_labels.background.color = "#EFFBFC",
    table.font.color = "#323232",
    table_body.hlines.color = "#989898",
    table_body.border.top.color = "#989898",
    heading.border.bottom.color = "#989898",
    table.width = "70%"
  ) %>%
  gt::opt_all_caps()

migration_table_new_app
write.csv(migration_table_new_app, "data/migration_table_new_appy.csv", row.names = FALSE)
```
:::
